%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{1em}{}[\color{black}\titlerule \vspace{3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jake Ryan} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{ssultan007@icloud.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
    \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Calgary}{Calgary, AB}
      {Bachelor of Finance, Minor in Computer Science | GPA: 3.64}{Sep. 2022 -- Dec. 2026} 
    \resumeSubheading
      {\textbf{Relevant Courses}}{}
      {\parbox{\textwidth}{%
        Programming in Python (A-), 
        Object-Oriented Programming in Java (A+),   
        Data Structures and Algorithms (In Progress), 
        Software Engineering (In Progress), 
        Artificial Intelligence and Machine Learning (Spring)
      }}{}
  \resumeSubHeadingListEnd

\vspace{-1pt}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Full-Stack Software Developer}{Jan 2025 -- Present}
      {TechStart Club}{University of Calgary, AB}
      \resumeItemListStart
        \resumeItem{contributed to the migration from React to Next.js, utilizing its SSR capabilities to improve SEO and initial page load times.}
        \resumeItem{Integrated Stripe API to handle payments, reducing transaction time by 2 minutes compared to Google Forms, leading to an enhanced user experience.}
         \resumeItem{Implemented Server-Side Rendering (SSR) with Next.js, enhancing SEO performance by pre-rendering dynamic content on the server.}
        \resumeItem{Collaborated within a team of five, enforcing Git best practices to ensure zero bugs were pushed to the main branch, resulting in higher code quality and smoother releases.}
      \resumeItemListEnd


       \resumeSubheading
      {UX/UI mentor}{Sep 2024 -- Jan 2025}
      {TechStart Club}{University of Calgary, AB}
      \resumeItemListStart
        \resumeItem{Mentored by a graduate UX/UI designer on best design practices, then guided TechStart’s project members to improve design skills and implement agile UX/UI development, ensuring high-quality User experience and interfaces for their final project showcase.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{OOP Pacman with smart ghost pathing} $|$ \emph{Java, JavaFX}}{Date -- Present}
          \resumeItemListStart
            \resumeItem{Researched the real Pacman game logic and successfully recreated all elements of the game.}
            \resumeItem{Created a Figma diagram to visualize the game logic and inheritance structure for easier collaboration.}
            \resumeItem{Contributed to  ~85\% of the codebase, handling complex parts, leaving the GUI and pellets to teammates.}
            \resumeItem{Designed a responsive GUI to sync with a backend 2D char array, helping less experienced teammates contribute.}
            \resumeItem{Developed ghost AI using a HashMap to store directions and tile positions, then filtering to the best move at a O(1) time complexity.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Personal Portfolio} $|$ \emph{Next.js, Motion, Playwright, Typescript, Figma Tailwind CSS, Aceternity UI, React}}{Date -- Present}
          \resumeItemListStart
            \resumeItem{Developed a personal site using Next.js 15, TypeScript, and Aceternity UI, achieving 97\% in performance, 93\% in best practices and 91\% in SEO according to pagespeed.web.dev.}
            \resumeItem{Designed a Figma prototype for the frontend, streamlining development and reducing style-related code changes by 90\%, accelerating UI iteration speed.}
            \resumeItem{Enabled project card additions with dedicated URL pages without modifying the codebase by leveraging React props and Next.js Dynamic Routes, eliminating codebase updates by 100\% reduction and improving scalability for near unlimited projects.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, TypeScript, Python, C, JavaScript, HTML/CSS, R} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, JUnit, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Visual Studio, PyCharm, IntelliJ} \\
     \textbf{Libraries}{: Aceterny UI, ShadCN UI, Material-UI,} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
